---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Ziqi Zhu
thanks: "Code and data are available at: https://open.toronto.ca/dataset/marriage-licence-statistics/."
date: 19 September 2024
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(ggplot2)
library(dplyr)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
```


# Introduction

You can and should cross-reference sections and sub-sections. We use @talia, @opendatatorotno, and @rohan.

The remainder of this paper is structured as follows. @sec-mydatasection


# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-marriage
#| fig-cap: Bills of penguins
#| echo: false

ggplot(data, aes(x = date, y = marriage_licenses, color = civic_centre, group = civic_centre)) +
  geom_line() +
  labs(title = "Marriage Licenses Over Time by Civic Centre",
       x = "Date",
       y = "Number of Marriage Licenses",
       color = "Civic Centre") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Talk more about it.


# Discussion

## First discussion point {#sec-first-point}


## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details


# References


