---
title: "Relation between number of Marriage and time"
subtitle: "a simple discussion of marriage number in Toronto"
author: 
  - Ziqi Zhu
thanks: "Code and data are available at: https://open.toronto.ca/dataset/marriage-licence-statistics/."
date: 19 September 2024
date-format: long
abstract: "This paper introduce the chage of number of marriage along time in Toronto briefly."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(ggplot2)
library(dplyr)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
```


# Introduction

We use @talia, and @opendatatorotno to discover some relation bwtween time and number of marriage in Toronto, here is some of my findings.


# Data {#sec-data}

Our data comes from open data Toronto.

```{r}
#| label: fig-marriage
#| fig-cap: Bills of penguins
#| echo: false

ggplot(data, aes(x = date, y = marriage_licenses, color = civic_centre, group = civic_centre)) +
  geom_line() +
  labs(title = "Marriage Licenses Over Time by Civic Centre",
       x = "Date",
       y = "Number of Marriage Licenses",
       color = "Civic Centre") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()
```


# Discussion

## First discussion point {#sec-first-point}
We can find from the graph that the number of marriage follow some same patterns for different regions like a wave, but after 2020, the number is unstable like previous years, there's a grow in general for most civic center, ET civic center is missing from the dataset since 2021.

## Second discussion point

An intresting point is the marriage number tends to be higher in some months, like summer and fall instead of some other months

\newpage

\appendix

# Appendix {-}


# Additional data details


# References


